---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# mirai.promises

**This package is archived as promises implemented by `mirai >= 1.0.0` are superior to the ones provided here. The more efficient, next generation promises in `mirai` are completely event-driven and non-polling, allowing for higher scalability and lower latency.**

`mirai.promises` makes 'mirai' 'promises' for easy integration in 'plumber' or 'shiny' pipelines.

`mirai.promises` also makes [`nanonext`](https://cran.r-project.org/package=nanonext) 'recvAio' 'promises', working on asynchronous message receives.

`mirai` >= 0.11.1 already supports 'promises' out of the box. In this case, loading `mirai.promises` after `mirai` will mask the equivalent method to provide additional functionality offered by this package such as allowing a custom polling interval.

### Installation

Install the latest release from CRAN:

```{r cran, eval=FALSE}
install.packages("mirai.promises")
```

Or the development version from R-universe:

```{r runiv, eval=FALSE}
install.packages("mirai.promises", repos = "https://shikokuchuo.r-universe.dev")
```

### Polling Interval

`polling()` may be used to customise the frequency with which to poll for promise resolution (defaults to every 100 ms).

Package authors wishing to use the S3 methods contained within this package may simply import the `polling()` function to make them available.

### Example

The below example simulates a plot function requiring a long compute in a 'shiny' app.

This app takes c. 2s to start compared to the 8s it would otherwise take if the ‘long-running’ computations were not running on parallel workers.

```{r example, eval=FALSE}
library(shiny)
library(mirai)
library(promises)
library(mirai.promises)

polling(freq = 50L)

# set 4 persistent workers
daemons(n = 4L)

ui <- fluidPage(
  fluidRow(
    plotOutput("one"),
    plotOutput("two"),
  ),
  fluidRow(
    plotOutput("three"),
    plotOutput("four"),
  )
)

make_plot <- function(time) {
  Sys.sleep(time)
  runif(10)
}

args <- list(make_plot = make_plot, time = 2)

server <- function(input, output, session) {
  output$one <- renderPlot(mirai(make_plot(time), .args = args) %...>% plot())
  output$two <- renderPlot(mirai(make_plot(time), .args = args) %...>% plot())
  output$three <- renderPlot(mirai(make_plot(time), .args = args) %...>% plot())
  output$four <- renderPlot(mirai(make_plot(time), .args = args) %...>% plot())
  session$onSessionEnded(stopApp)
}

shinyApp(ui = ui, server = server)
```

### Thanks

[Joe Cheng](https://github.com/jcheng5) for optimising the promises method to work seamlessly within Shiny.

[Daniel Falbel](https://github.com/dfalbel/) for the original version of the above example and agreeing to its use here, as well as the specific use case that motivated this package.

### Links

`mirai.promises` on CRAN: <https://cran.r-project.org/package=mirai.promises>

`mirai` website: <https://shikokuchuo.net/mirai/><br />
`mirai` on CRAN: <https://cran.r-project.org/package=mirai><br />
&nbsp;&nbsp;- High Performance Computing CRAN Task View: <https://cran.r-project.org/view=HighPerformanceComputing>

`nanonext` website: <https://shikokuchuo.net/nanonext/><br />
`nanonext` on CRAN: <https://cran.r-project.org/package=nanonext>

--

### Code of Conduct

Please note that the mirai.promises project is released with a [Contributor Code of Conduct](https://contributor-covenant.org/version/2/1/CODE_OF_CONDUCT.html). By contributing to this project, you agree to abide by its terms.
