---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# mirai.promises

<!-- badges: start -->
[![CRAN status](https://www.r-pkg.org/badges/version/mirai.promises?color=112d4e)](https://CRAN.R-project.org/package=mirai.promises)
[![mirai.promises status badge](https://shikokuchuo.r-universe.dev/badges/mirai.promises?color=24a60e)](https://shikokuchuo.r-universe.dev) 
<!-- badges: end -->

`mirai.promises` allows the use of 'mirai' as 'promises' for easy integration in 'plumber' or 'shiny' pipelines.

### Installation

Install the latest release from CRAN:

```{r cran, eval=FALSE}
install.packages("mirai.promises")
```

or the development version from rOpenSci R-universe:

```{r runiv, eval=FALSE}
install.packages("mirai.promises", repos = "https://shikokuchuo.r-universe.dev")
```

### Links

`mirai` website: <https://shikokuchuo.net/mirai/><br />
`mirai` on CRAN: <https://cran.r-project.org/package=mirai>

Listed in CRAN Task View: <br />
- High Performance Computing: <https://cran.r-project.org/view=HighPerformanceComputing>

--

Please note that this project is released with a [Contributor Code of Conduct](https://shikokuchuo.net/mirai.promises/CODE_OF_CONDUCT.html). By participating in this project you agree to abide by its terms.
